Tutorial for Runing Mouse Bone Marrow Dataset

### 2023-10-20 Demo_marrow_facs.Rmd

```{r}
df_module = data.frame(Module = levels(gene_partition))
df_module[,"Gene"] = unlist(lapply(levels(gene_partition),function(x){paste(names(gene_partition)[gene_partition == x],collapse = ",")}))
df_module[,"celltype"] = module_celltype[levels(gene_partition)]
df_module[top_go_clusters,"GO_description"] = unlist(lapply(top_enrich_go,function(x) paste(x[['Description']],collapse = ",")))
df_module[top_pathway_clusters,"Pathway_description"] = unlist(lapply(top_enrich_pathway,function(x) paste(x[['Description']],collapse = ",")))
df_module[is.na(df_module)] = ""
write.csv(df_module,file = "module_description.csv",row.names = FALSE)
```

>>>>

```{r}
df_module = data.frame(Module = levels(gene_partition))
df_module[,"Gene"] = unlist(lapply(levels(gene_partition),function(x){paste(names(gene_partition)[gene_partition == x],collapse = ",")}))
df_module[,"celltype"] = module_celltype[levels(gene_partition)]
df_module[top_go_clusters,"GO_description"] = unlist(lapply(top_enrich_go,function(x){
  des = x[["Description"]]
  paste(des[!is.na(des)],collapse = ",")
}
))
df_module[top_pathway_clusters,"Pathway_description"] = unlist(lapply(top_enrich_pathway,function(x){
  des = x[["Description"]]
  paste(des[!is.na(des)],collapse = ",")
}))
df_module[is.na(df_module)] = ""
write.csv(df_module,file = "./marrow_result/module_description.csv",row.names = FALSE)
```

## Cell Cycle Modules
```{r}
library(gprofiler2)
mmus_s = gorth(cc.genes.updated.2019$s.genes, source_organism = "hsapiens", target_organism = "mmusculus")$ortholog_name
mmus_g2m = gorth(cc.genes.updated.2019$g2m.genes, source_organism = "hsapiens", target_organism = "mmusculus")$ortholog_name
tiss = CellCycleScoring(tiss, s.features = mmus_s, 
                        g2m.features = mmus_g2m, set.ident = FALSE)
DimPlot(tiss,group.by = "Phase")

pdf(width = 30, height = 5)
pl
dev.off()
```
